A Phenomenological Model for the Intra-Cluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-09-23 paper1.tex
added X-ray subsections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{X-ray scaling relations and luminosity function}
\label{sec:4}

In order to check whether our phenomenologically derived gas profiles reproduce
the observations, we calculate the bolometric thermal bremsstrahlung
luminosity $L_{\rmn{bol}}$ as in \cite{1988xrec.book.....S}\footnote{We check
  our procedure by fitting each of the 31 REXCESS clusters with
  equation~(\ref{eq:gnfw}) and calculating $L_{\rmn{bol}}$ with the measured gas
  temperature of each cluster. As a result, we fall short of the observed
  luminosity by a mean (median) of about $21\%$ ($20\%$). This is reasonable
  considering that we do not permit the parameters $R_{\rmn{c}}$, $\alpha$ and
  $\delta$ to vary between different objects. Additionally, we neglect atomic
  line emission which may give a noticeable contribution, in particularly for
  low-mass clusters and in the cluster outskirts of larger systems.}  and
compare our sample result with the observed $L_{\rmn{bol}} - M_{500}$ relation
and XLF.\footnote{The mean (median) difference at $z=0$ between
  $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5\%$ ($\approx
  7\%$). While $L_{\rmn{bol}}$ refers to the quantity calculated within
  $R_{500}$, we note that the XLF for luminosities calculated within $R_{200}$
  will be barely changed.}

To assign a temperature to our model clusters (that is needed for calculating
$L_{\rmn{bol}}$ and $Y_{\rmn{X}}$), we adopt the $T-M_{500}$ relation by
\cite{2010MNRAS.406.1773M},
\begin{equation}
\log_{10} \left( \frac{k_{\rmn{B}}T_{\rmn{ci}}}{\rmn{keV}} \right) = 
A + B~\log_{10} \left( \frac{E(z) M_{500}}{10^{15} h_{70}^{-1} \rmn{M_{\odot}}} \right)
\label{eq:temp}
\end{equation}
where $A=0.91$, $B=0.46$, and $T_{\rmn{ci}}$ is the cluster temperature
\emph{not} centrally excised
(\citealp{2010MNRAS.406.1773M}). \cite{2010MNRAS.406.1773M} report a scatter of
$\sigma_{\rmn{yx}} = 0.06,$\footnote{Scatter is calculated as $\sigma_{\rmn{yx}}
  = \sqrt{ \left\{ \Sigma_{i=1}^{N} [Y_{i}-(A+B~X_{i})]^{2}\right\} / N-1}$
  where the sum extends over the data points $X_{i}, Y_{i}$, and $A$ and $B$ are
  the fit parameters.} which we apply to our sample using Gaussian deviates.

@@

\subsection{X-ray Luminosity Function}
Studies of the XLF got out of fashion during the last years due to the
difficulties of using the X-ray luminosity for cosmological purposes. The X-ray
emissivity scales with the square of the gas density, which makes it subject to
density variations and clumping. This implies large scatter that causes a large
Malmquist bias and underlines the necessity of careful mock surveys that need to
address all systematics.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{X-ray  observables}
\label{sec:4}

So far, we used a well-observed representative sample of X-ray clusters
(REXCESS) that was supplemented by X-ray data on gas mass fractions to construct
our phenomenological gas model.  Here, we will test how our cluster mock data
compares to various X-ray inferred observables. Those include the observed
$L_{\rmn{bol}} - M_{500}$ relation, the $Y_X - M_{500}$ relation, and the
XLF.

\subsection{Scaling Relations}

First, we calculate the bolometric thermal bremsstrahlung luminosity
$L_{\rmn{bol}}$ following \cite{1988xrec.book.....S}.\footnote{We check our
  procedure by fitting each of the 31 REXCESS clusters with
  equation~(\ref{eq:gnfw}) and calculating $L_{\rmn{bol}}$ with the measured gas
  temperature of each cluster. As a result, we fall short of the observed
  luminosity by a mean (median) of about $21\%$ ($20\%$). This is reasonable
  considering that we do not permit the parameters $R_{\rmn{c}}$, $\alpha$ and
  $\delta$ to vary between different objects. Additionally, we neglect atomic
  line emission which may give a noticeable contribution, in particularly for
  low-mass clusters and in the cluster outskirts of larger systems.}  To assign
a temperature to our model clusters (that is needed for calculating
$L_{\rmn{bol}}$ and $Y_{\rmn{X}}$), we adopt the $T-M_{500}$ relation by
\cite{2010MNRAS.406.1773M},
\begin{equation}
\log_{10} \left( \frac{k_{\rmn{B}}T_{\rmn{ci}}}{\rmn{keV}} \right) = 
A + B~\log_{10} \left( \frac{E(z) M_{500}}{10^{15} h_{70}^{-1} \rmn{M_{\odot}}} \right)
\label{eq:temp}
\end{equation}
where $A=0.91$, $B=0.46$, and $T_{\rmn{ci}}$ is the cluster temperature
\emph{not} centrally excised
(\citealp{2010MNRAS.406.1773M}). \cite{2010MNRAS.406.1773M} report a scatter of
$\sigma_{\rmn{yx}} = 0.06,$\footnote{Scatter is calculated as $\sigma_{\rmn{yx}}
  = \sqrt{ \left\{ \Sigma_{i=1}^{N} [Y_{i}-(A+B~X_{i})]^{2}\right\} / N-1}$
  where the sum extends over the data points $X_{i}, Y_{i}$, and $A$ and $B$ are
  the fit parameters.} which we apply to our sample using Gaussian deviates.

@@

\subsection{Luminosity Functions}
Studies of the XLF got out of fashion during the last years due to the
difficulties of using the X-ray luminosity for cosmological purposes. The X-ray
emissivity scales with the square of the gas density, which makes it subject to
density variations and clumping.\footnote{The mean (median) difference at $z=0$
  between $L_{\rmn{bol}}$ within $R_{200}$ or within $R_{500}$ is $\approx 5\%$
  ($\approx 7\%$). While $L_{\rmn{bol}}$ refers to the quantity calculated
  within $R_{500}$, we note that the XLF for luminosities calculated within
  $R_{200}$ will be barely changed.} This implies large scatter that causes a
large Malmquist bias and underlines the necessity of careful mock surveys that
need to address all systematics.
